### 2020-01-16 methods.tex
discussion of GPT2 added
normalization discussion added

where $\lambda_{i}$ is the $i-th$ eigenvalue of the correlation matrix $\mathbf{X}=\dfrac{1}{N}\mathbf{W}^{T}\mathbf{W}$, and $\lambda_{max}$ is the maximum eigenvalue.   (Note that eigenvalues are the square of the singular values $\sigma_{i}$ of $\mathbf{W}$ :  $\lambda_{i}=\sigma^{2}_{i}$.)

@@

SOME MORE DISCUSSION HERE

@@

>>>>

where $\lambda_{i}$ is the $i-th$ eigenvalue of the \emph{Empirical Correlation Matrix}

\begin{equation}
\mathbf{X}=\mathbf{W}^{T}\mathbf{W}
\end{equation}

and $\lambda_{max}$ is the maximum eigenvalue. These eigenvalues are the square of the singular values $\sigma_{i}$ of $\mathbf{W}$ :  $\lambda_{i}=\sigma^{2}_{i}$.

@@

@@

\paragraph{Normalization of Empirical Matrices}.  Formally, to apply RMT, we would usually define Correlation Matrix with $\dfrac{1}{N}$ normalization,
and assume that either the variance of $\mathbf{X}$ is unity, $\sigma^{2}=1$, or is known.
\footnote{And for formal proofs of the Heavy Tailed results, we need a different normalization,$\dfrac{1}{N^{1-\alpha}}$}
But for these empirical studies, the pretrained DNNs are typically initialized with random weight matrices $\mathbf{W}_{0}$ ,
with the variance already normalized to $\sqrt{\frac{1}{N}}$, or some variant of this such as Glorot (or Xavier) Normalization\cite{GloRot},
or as $\sqrt{\frac{2}{N*k^2}}$ for Convolutional 2D Layers. 
We do not normalize (or renormalize) the Empirical Correlation Matrices, and use them as-is,
except that we rescale the Conv2D pre-Activation Maps $\mathbf{W}_{i,L}$ by $\frac{k}{\sqrt{2}}$ so that they
are on the same scale as the Linear layers.
Note that in some pretrinaed models, like the pyTorch VGG models, the Linear weight matrices appear to have been 
initialized with variance $\sigma\sim0.01$.  We do not attempt to correct for this, and, instead, simply try to treat all
models the same.  
Also, The normalization does not affect the Power Law fits because the Heavy Tailed exponent $\alpha$ is scale-invariant.
As are metrics like the Stable Rank and our MP Soft Rank. In this study, however, all of the metrics strongly depend 
on the scale of the weight matrix.

\paragraph{The WeightWatcher Tool}
